Agile Inter-team Software Development

### 2019-01-21 Draft/Parts/Main.tex
Finish pass on main text.

\section{Communication Concerns}\label{sec:spt_ex} 
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%social fixes
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribes work will occur.
%second problem
Consider another scenario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads  \cite{kniberg12}.

\section{Supporting Communication in Inter-team Development}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at different levels need to have ways to pass information.
This can be addressed by adaptions in development process and leveraging technology.
Second, the quality of communication needs to be accurate.
This can be addressed by sound system specification through architecture and design.
%In Section ~\ref{sec:proc_impv}, we discuss the adaptations to an agile process, and team structure, to support better collaboration between teams.
%In Section ~\ref{sec:tech_impv}, we discuss the ways in which technology improve inter-team communication
%In Section ~\ref{sec:imp_of_dsgn}, we discuss the role of architecture and design in mitigating communication issues.

\subsection{Process Improvements} 
\label{sec:proc_impv}
	There are many small changes \cite{collabAcrossAgile_article} that we can incorporate in our process model to make sure that parallel developing agile teams do not run into problems when they reach the integration phase.
	These changes are to be made part of the entire process.

%Changes in standups
	One of the most critical aspect of agile process model is to have daily standups which are the platform serving the purpose of letting each team member know the work being done in the other parts of the team and correlate it with the work being done by them.
	This results in escalation of differences between the development early in the process and prevents end moment discovery of mismatches in interfaces and such.
	In the case of multiple agile teams this problem is compounded as usually a daily stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
	This can be resolved by having a representative of each concerned team being present in the daily standup thus letting each team know the status of other teams.

%Changes to Product Owner
Though in usual implementations the product owner is responsible for agile teams under his supervision, in large projects with multiple agile teams where a number of product owners are present sometimes over time the vision of the owners may get too distinct from each other thus pushing the development track in different directions.
This can be limited by having regular meetings of product owners where the scope and vision of the project could be synced again. This can be a bi-weekly or monthly meeting depending on the size of the project.

%Changes in Planning Sessions
All the initial, intermediate and final planning sessions should be made such that all the teams which are or could be impacted by that part of the project are part of the meeting.
This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.

\subsection{Technology Approaches} \label{sec:tech_impv}
Selecting an appropriate technology stack plays an important role maintaining a widely distributed team.
Technology can help teams in keeping track of things that they need to do so that other teams can work efficiently.
The following are some of the areas where the technology can enable a more efficient agile process environment.

%Communication Tools
Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can help the team interactions become more fluid and clearer.
They also make the communication real-time thus removing the delay in process due to time spent in communicating ideas across teams.
%Integration Tools
Continuous integration tools can go a long way in finding out inter-team problems early in the process as every time any team makes a change, its impact on the entire project can be seen.

\subsection{Importance of Architecture/Design}\label{sec:imp_of_dsgn}
%Why is Design/Architecture so important when doing this?

As we know that the product owner in an agile process model is the person with the vision of what the project will look like and if it is a small team the product owner can clearly pass this to each and every member of the team and even each member can query the product owner directly when in doubt.
But in large scale projects where multiple agile teams are working together in supervision of a few product owners it is practically impossible for the owner to keep doing what they did in a small team, that’s where a formal definition of their vision comes in handy as it enables the teams to look up to something when encountering a design decision.
The design or architecture in this case acts as a common vision for not only the teams but also for the communication between all the product owners.
The design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} as when the teams can’t come to a common consensus the design shows the path to take.
%non specification fix
Spotify addresses this issue with a more organizational approach by defining a "system owner" role \cite{kniberg12}.
This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.

In addition to specification of system elements, architecture can also be used to empower teams.
As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
The latter approach ideal for agile development since this approaches defines system components in terms of design decisions, which empowers individual teams.

>>>>

\section{Communication Concerns}\label{sec:spt_ex} 
%overview
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
% problem
Consider a scenario at Spotify \cite{kniberg12}: a tester on a particular agile team invested time to solve a particular problem, which was also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters, which are crosscutting divisions which gathers individuals with similar roles across different Squads. 
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribe's work will occur.
%Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.
%todo: any more issues? Dunbar

In general, consistency becomes as issue when expanding to multiple teams.
The product owner in an agile process model is the person with the project vision and if it is a small team the product owner can clearly communicate this to every team member.
Members can even query the product owner directly when in doubt.
However, in large scale projects where multiple teams are working together, it is practically impossible for the owner to keep doing what they did in a small team.
That’s where a formal definition of their vision is useful as it gives teams something to consult to when encountering a design decision.

\section{Supporting Communication in Inter-team Development}
\label{sec:prop_appro} 
The general problem of communication can be tackled from two perspectives.
First, stakeholders at and across different levels need to have communication channels.
This can be addressed by adaptations in development process and leveraging technology.
Second, the quality (e.g., accuracy) of communication needs to be high.
This can be addressed by thorough system specification through architecture and design.

\subsection{Process Adaptations} 
\label{sec:proc_impv}
	There are many changes \cite{collabAcrossAgile_article} that can be incorporated into a process model to decrease the chance that parallel agile teams run into problems during integration.

%Changes in standups
One critical aspect of an agile process is daily standups which are a platform for letting each team member know the work being done in other parts of the team and correlate it with the work they are performing.
This uncovers differences in understanding early in development and prevents last minute discovery of mismatches in development.
In the case of multiple agile teams this problem is compounded as a stand up is a closed activity of the team itself, thus preventing other teams from knowing the results or discussions of each other.
This can be resolved by having a representative of each concerned team be present in the daily standup thus letting each team know the status of the other teams.

%Changes to Product Owner
Although the product owner is responsible for agile teams under his supervision, projects with multiple agile teams may have multiple product owners, and over time the vision of the owners may drift and lead the development in different directions.
This can be limited by having regular meetings of product owners where the scope and vision of the project can be synchronized.
%This can be a bi-weekly or monthly meeting depending on the size of the project.

%Changes in Planning Sessions
All the initial, intermediate and final planning sessions should be made such that teams which are or could be impacted by that part of the project are part of the meeting.
This can assist in early agreement on high-level requirements and standardization of inter-team interfaces.

\subsection{Technology Improvements} \label{sec:tech_impv}
Selecting an appropriate technology stack plays an important role in maintaining a distributed development environment.
Technology enables communication and task management so that teams can work together efficiently.
%The following are areas where technology can enable a more efficient agile process.

%Communication Tools
Since agile focuses on personal interaction, particularly face-to-face conversation, video conferencing tools can lower the bar to inter-team interactions.
They also make communication real-time, reducing delay due to time spent in communicating ideas across teams.
%Integration Tools
Continuous integration tools can go a long way in identifying inter-team problems early in development
as it reveals the impact of changes on the entire project.

\subsection{Importance of Architecture and Design}\label{sec:imp_of_dsgn}
%Why is Design/Architecture so important when doing this?

System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners.
The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
%non specification fix
A second approach addresses this issue from an organizational standpoint by defining a "system owner" role \cite{kniberg12}.
This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.

In addition to specification, proper architecture can also be used to enable team agility.
As discussed by Parnas \cite{Parnas72}, there are two general approaches to decomposing systems: 1) compartmentalizing a computational process and, 2) focusing on information hiding.
The latter approach is ideal for agile development since it defines system components in terms of hiding design decisions, which empowers individual teams to design their own solution.
